Unlocking Accountability: A Mixed-Methods Analysis of Bottom-Up Approaches in Brazilian Public Policy

### 2023-10-27 Scripts/paper.Rmd
fixing path issue

load(here("obra_transparente", "Dados", "obras_inicio_projeto.Rdata"))
load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

# load(here("Dados", "obras_inicio_projeto.Rdata"))
# load(here("Dados", "obras_fim_seg_fase.Rdata"))

simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
# simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")

load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

df_cidades_ot <- read_excel("Dados/181114 - Situação obras_atual.xlsx", 
                                           sheet = "SIMEC-Mai17", skip = 1) %>%
  clean_names() %>%
  filter(!is.na(id)) %>%
  dplyr::select(id, municipio, uf, situacao2, levant_os_jun_17) %>%
  mutate(indicator_ot = 1)
```

>>>>

# load(here("obra_transparente", "Dados", "obras_inicio_projeto.Rdata"))
# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

load(here("Dados", "obras_inicio_projeto.Rdata"))
load(here("Dados", "obras_fim_seg_fase.Rdata"))

# simec23 <- fread(here("obra_transparente", "Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")
simec23 <- fread(here("Dados", "simec 25-10-23 - simec.csv"), encoding = "UTF-8")

# load(here("obra_transparente", "Dados", "obras_fim_seg_fase.Rdata"))

load(here("Dados", "obras_fim_seg_fase.Rdata"))

df_cidades_ot <- read_excel(here("Dados", "181114 - Situação obras_atual.xlsx"), 
                                           sheet = "SIMEC-Mai17", skip = 1) %>%
  clean_names() %>%
  filter(!is.na(id)) %>%
  dplyr::select(id, municipio, uf, situacao2, levant_os_jun_17) %>%
  mutate(indicator_ot = 1)
```
